---
title: "CMP_DataWrangling"
author: "Caroline Newell"
date: "3/28/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---


#Step 1
Isolate the data sheet from each sample set from SIF.
Note: Use corrected sheets for CMPKrabby, POM_VOL_1, 2, 3, 4, 5, CMPZoopSoup, CMPSmallFry, CMPeas, CMPhragmites, CMPLiverRoast, CMPLeftovers.
 
##Load packages
```{r}
library(readxl)
library(tidyverse)
library(stringr)
library(lubridate)
```

# Read in metadata
```{r}
#Fish
FishInfo_040122 <- read_excel("Data/FishInfo_040122.xlsx")

LargeMacroinvetInfo_040322 <- read_excel("Data/LargeMacroinvetInfo_040322.xlsx")

CMP_SmallMacroinvertInfo_04022022 <- read_excel("Data/CMP_SmallMacroinvertInfo_04022022.xlsx")

PlantInfo_121721 <- read_excel("Data/PlantInfo_121721.xlsx")

POM_BENTHIC_Info <- read_excel("Data/POM_BENTHIC_Info.xlsx")

ZoopInfo <- read_excel("Data/ZoopInfo.xlsx")
```

#Read in all the isotope data sheets
### CN

Note: Not reading in the GlassHalfFull or POMParty data since they were test runs and data not useful.

```{r}
CMPandemic_CN <- read_excel("Data/SIF-CN/DataOnly/CMPandemic_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
View(CMPandemic_CN)

CMPeas_CN<-  read_excel("Data/SIF-CN/DataOnly/CMPeas_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",  "numeric", "numeric", "numeric"))
glimpse(CMPeas_CN)

CMPFish4Ever_CN <- read_excel("Data/SIF-CN/DataOnly/CMPFish4Ever_CN.xls", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",  "numeric", "numeric", "numeric"))
glimpse(CMPFish4Ever_CN)

CMPFishRFriends_CN <- read_excel("Data/SIF-CN/DataOnly/CMPFishRFriends_CN.xls", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric",       "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPFishRFriends_CN)

CMPflanzen_CN <- read_excel("Data/SIF-CN/DataOnly/CMPflanzen_CN_edited.xlsx", col_types = c("text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",     "numeric", "numeric", "numeric"))
View(CMPflanzen_CN) #Are these all tapwater? Can I put in "tap" treatment so it aligns with CMPhragmites?

CMPhragmites_CN <- read_excel("Data/SIF-CN/DataOnly/CMPhragmites_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",     "numeric", "numeric", "numeric"))
glimpse(CMPhragmites_CN)

CMPKrabby_CN <- read_excel("Data/SIF-CN/DataOnly/CMPKrabby_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPKrabby_CN)

CMPLeftovers_CN <- read_excel("Data/SIF-CN/DataOnly/CMPLeftovers_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPLeftovers_CN)

CMPLiverLaVida_CN <- read_excel("Data/SIF-CN/DataOnly/CMPLiverLaVida_CN.xls", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPLiverLaVida_CN)

CMPLiverLetDie_CN <- read_excel("Data/SIF-CN/DataOnly/LiverLetDie_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(CMPLiverLetDie_CN)

CMPLiverPool_CN <- read_excel("Data/SIF-CN/DataOnly/CMPLiverPool_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPLiverPool_CN)

CMPLiverRoast_CN <- read_excel("Data/SIF-CN/DataOnly/CMPLiverRoast_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPLiverRoast_CN)

CMPLiverWorst_CN <- read_excel("Data/SIF-CN/DataOnly/CMPLiverWorst_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPLiverWorst_CN)

CMPMuscleBob_CN <- read_excel("Data/SIF-CN/DataOnly/CMPMuscleBob_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPMuscleBob_CN)

CMPMuscleStuffin_CN <- read_excel("Data/SIF-CN/DataOnly/CMPMuscleStuffin_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",        "numeric", "numeric", "numeric"))
glimpse(CMPMuscleStuffin_CN)

CMPMysteryMeat_CN <- read_excel("Data/SIF-CN/DataOnly/CMPMysteryMeat_CN.xls", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",     "numeric", "numeric", "numeric"))
glimpse(CMPMysteryMeat_CN)

CMPSilenceOThLab_CN <- read_excel("Data/SIF-CN/DataOnly/CMPSilenceOThLab_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPSilenceOThLab_CN)

CMPSkrimp_CN <- read_excel("Data/SIF-CN/DataOnly/CMPSkrimp_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPSkrimp_CN)

CMPSkrimp2_CN <- read_excel("Data/SIF-CN/DataOnly/CMPSkrimp2_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPSkrimp2_CN)

CMPSmallFry_CN <- read_excel("Data/SIF-CN/DataOnly/CMPSmallFry_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPSmallFry_CN)

CMPTheGovernator_CN <- read_excel("Data/SIF-CN/DataOnly/CMPTheGovernatorCN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPTheGovernator_CN)

CMPVeryStable_CN <- read_excel("Data/SIF-CN/DataOnly/CMPVeryStable_CN.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPVeryStable_CN)

CMPZoopSoup_CN <- read_excel("Data/SIF-CN/DataOnly/CMPZoopSoup_TotalCNcorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "numeric", "numeric", "numeric"))
glimpse(CMPZoopSoup_CN)

PomVol1_CN <- read_excel("Data/SIF-CN/DataOnly/POMVol1_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(PomVol1_CN)

PomVol2_CN <- read_excel("Data/SIF-CN/DataOnly/POMVol2_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(PomVol2_CN)

PomVol3_CN <- read_excel("Data/SIF-CN/DataOnly/POMVol3_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(PomVol3_CN)

PomVol4_CN <- read_excel("Data/SIF-CN/DataOnly/POMVol4_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(PomVol4_CN)

PomVol5_CN <- read_excel("Data/SIF-CN/DataOnly/POMVol5_TotalCNCorrected.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric",   "numeric", "numeric", "numeric"))
glimpse(PomVol5_CN)
```

Next: flag rows of samples where samples were lost (mixed up or destroyed at SIF)
List of lost samples:
CMPFishRFriends: 199m, 200m, 201m, 202m
CMPSkrimp: CMP-INVERT-EXO82-CN, CMP-INVERT-EXO83-CN, CMP-INVERT-EXO84-CN, CMP-INVERT-EXO85-CN, CMP-INVERT-EXO86-CN, CMP-INVERT-EXO87-CN, CMP-INVERT-HMC64-CN, CMP-INVERT-HMC65-CN, CMP-INVERT-HMC66-CN, CMP-INVERT-HMC67-CN, CMP-INVERT-HMC68-CN, CMP-INVERT-HMC69-CN, CMP-INVERT-HMC70-CN, CMP-INVERT-HMC71-CN, CMP-INVERT-HMC13-CN, CMP-INVERT-HMC14-CN, CMP-INVERT-HMC17-CN, CMP-INVERT-HMC18-CN, CMP-INVERT-HMC16-CN, CMP-INVERT-HMC27-CN, CMP-INVERT-HMC26-CN, CMP-INVERT-HMC25-CN, CMP-INVERT-HMC30-CN, CMP-INVERT-HMC28-CN, CMP-INVERT-HMC21-CN, CMP-INVERT-HMC29-CN, CMP-INVERT-HMC15-CN, CMP-INVERT-EXO40-CN, CMP-INVERT-EXO41-CN, CMP-INVERT-EXO42-CN, CMP-INVERT-EXO26-CN, CMP-INVERT-EXO25-CN, CMP-INVERT-EXO24-CN, CMP-INVERT-EXO23-CN, CMP-INVERT-EXO44-CN, CMP-INVERT-EXO22-CN, CMP-INVERT-EXO45-CN, CMP-INVERT-EXO43-CN, CMP-INVERT-EXO15-CN, CMP-INVERT-EXO14-CN, CMP-INVERT-EXO13-CN, CMP-INVERT-EXO35-CN, CMP-INVERT-EXO19-CN, CMP-INVERT-EXO34-CN, CMP-INVERT-HMC22-CN, CMP-INVERT-RSC11-CN, CMP-INVERT-RSC15-CN, CMP-INVERT-RSC14-CN, CMP-INVERT-RSC2-CN, CMP-INVERT-RSC12-CN, CMP-INVERT-RSC10-CN, CMP-INVERT-RSC18-CN, CMP-INVERT-RSC16-CN, CMP-INVERT-RSC13-CN, CMP-INVERT-RSC3-CN, CMP-INVERT-RSC6-CN, CMP-INVERT-RSC17-CN, CMP-INVERT-RSC5-CN, CMP-INVERT-RSC9-CN, CMP-INVERT-RSC1-CN, CMP-INVERT-RSC7-CN, CMP-INVERT-RSC8-CN, CMP-INVERT-HMC19-CN, CMP-INVERT-HMC11-CN, CMP-INVERT-HMC10-CN, CMP-INVERT-HMC31-CN, CMP-INVERT-HMC23-CN, CMP-INVERT-HMC24-CN, CMP-INVERT-HMC32-CN, CMP-INVERT-HMC33-CN, CMP-INVERT-HMC34-CN, CMP-INVERT-HMC35-CN, CMP-INVERT-HMC20-CN, CMP-INVERT-HMC36-CN.
POMVol2: CMP-POM-150-CN, CMP-POM-151-CN

Other issues:
POMVol4: CMP-POM-51-CN <-"Mass 45 saturated; estimated value used"
POMVol4: CMP-POM-52-CN <- "Mass 44 & 45 saturated, totals underestimated"

May also want to remove samples with low C/N precision - Make them NA?

N TOO LOW: "Precision decreases for samples containing less than 20ugN"
POMVol1: CMP-POM-18-CN, CMP-POM-28-CN, CMP-POM-46-CN, CMP-POM-66-CN, CMP-POM-76-CN, CMP-POM-81-CN, CMP-POM-91-CN, CMP-POM-106-CN, CMP-POM-110-CN, CMP-POM-121-CN, CMP-POM-122-CN, CMP-POM-125-CN, CMP-POM-127-CN, CMP-POM-129-CN
POMVol2: CMP-POM-135-CN, CMP-POM-137-CN, CMP-POM-146-CN, CMP-POM-147-CN, CMP-POM-149-CN, CMP-POM-153-CN, CMP-POM-154-CN, CMP-POM-155-CN, CMP-POM-156-CN, CMP-POM-158-CN, CMP-POM-159-CN, CMP-POM-160-CN, CMP-POM-161-CN, CMP-POM-163-CN, CMP-POM-170-CN, CMP-POM-173-CN, CMP-POM-175-CN, CMP-POM-176-CN, CMP-POM-178-CN, CMP-POM-179-CN, CMP-POM-180-CN, CMP-POM-180-CN, CMP-POM-183-CN, CMP-POM-126rep-CN, CMP-POM-121rep-CN, CMP-POM-183rep-CN, CMP-POM-123rep-CN, CMP-POM-150rep-CN, CMP-POM-111rep-CN.
POMVol4: CMP-POM-36-CN, CMP-POM-38-CN, CMP-POM-40-CN, CMP-POM-93-CN, CMP-POM-94-CN, CMP-POM-171-CN
CMPeas:CMP-Plant45D-1-CN, CMP-Plant46T-2-CN, CMP-Plant46D-1-CN, CMP-Plant46D-2-CN, CMP-Plant42T-2-CN, CMP-Plant42T-3-CN, CMP-Plant42D-2-CN, CMP-Plant42D-3-CN, CMP-Plant47D-1-CN, CMP-Plant47D-2-CN, CMP-Plant47D-3-CN
CMPhragmites: CMP-Plant50D-2-CN, CMP-Plant55T-1-CN, CMP-Plant55T-2-CN, CMP-Plant55D-1-CN, CMP-Plant55D-2-CN, CMP-Plant55D-3-CN, CMP-Plant57T-3-CN, CMP-Plant57D-1-CN, CMP-Plant57D-2-CN, CMP-Plant57D-3-CN, CMP-Plant59T-1-CN, CMP-Plant59T-3-CN, CMP-Plant59D-2-CN, CMP-Plant59D-3-CN, CMP-Plant60T-2-CN, CMP-Plant60T-3-CN, CMP-Plant60D-1-CN, CMP-Plant60D-3-CN
CMPflanzen: CMP-Plant4-1-CN
CMPLiverWorst: CMP-FISH-694L-CN

"Contained less nitrogen than smallest reference"
CMPeas:CMP-Plant40T-3-CN
CMPhragmites: CMP-Plant57T-1-CN, CMP-Plant57T-2-CN, CMP-Plant59T-2-CN, CMP-Plant59D-1-CN
POMVol5: CMP-POM-38redo-CN

C TOO LOW ("Contained less carbon than smallest reference"):
POMVol1: CMP-POM-125-CN
POMVol4: CMP-POM-38-CN
POMVol2: CMP-POM-148-CN, CMP-POM-158-CN
POMVol5: CMP-POM-38redo-CN
Should separate C and N. 

CONTAINS MORE N THAN LARGEST REFERENCE:"Contained more nitrogen than largest reference"
CMPZoopSoup: CMP-Zoop-B5-CN
POMVol4: CMP-POM-51-CN, CMP-POM-52-CN, CMP-POM-192-CN
CMPLeftovers: CMP-FISH-778M-CN
CMPLiverPool: CMP-FISH-441L-CN
CMPVeryStable: CMP-FISH-428M-CN, CMP-FISH-505M-CN, CMP-FISH-494M-CN

CONTAINS MORE C THAN LARGEST REFERENCE: "Contained more carbon than largest reference"
POMVol4: CMP-POM-192-CN


###S
```{r}
CMPatty_S <- read_excel("Data/SIF-S/DataOnly/CMPatty_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPBuffPants_S <- read_excel("Data/SIF-S/DataOnly/CMPBuffPants_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPBuffPants_S)

CMPChoppedLiver_S <- read_excel("Data/SIF-S/DataOnly/CMPChoppedLiver_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))
glimpse(CMPChoppedLiver_S)

CMPeace_S <- read_excel("Data/SIF-S/DataOnly/CMPeace_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPeace_S)

CMPeachment_S <- read_excel("Data/SIF-S/DataOnly/CMPeachment_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPeachment_S)

CMPISeeDeadCMPeople_S <- read_excel("Data/SIF-S/DataOnly/ISeeDeadCMPeople_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPISeeDeadCMPeople_S)

CMPlants_S <- read_excel("Data/SIF-S/DataOnly/CMPlants_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPLiverGiver_S <- read_excel("Data/SIF-S/DataOnly/CMPLiverGiver_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPLiverItUp_S <- read_excel("Data/SIF-S/DataOnly/CMPLiverItUp_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))
glimpse(CMPLiverItUp_S)

CMPLiverLaughLov_S <- read_excel("Data/SIF-S/DataOnly/CMPLiverLaughLov_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPLiverLaughLov_S)

CMPLiverOfMine_S <- read_excel("Data/SIF-S/DataOnly/CMPLiverOfMine_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPLiverOfMine_S)

CMPlucheae_S <- read_excel("Data/SIF-S/DataOnly/CMPlucheae_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPMudBugs_S <- read_excel("Data/SIF-S/DataOnly/CMPMudBugs_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPMuscleMeat_S <- read_excel("Data/SIF-S/DataOnly/CMPMuscleMeat_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPNotFood_S <- read_excel("Data/SIF-S/DataOnly/CMPNotFood_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))
glimpse(CMPNotFood_S)

CMPoaceae_S <- read_excel("Data/SIF-S/DataOnly/CMPoaceae_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPSampler_S <- read_excel("Data/SIF-S/DataOnly/CMPSampler_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPSchwarzeneger_S <- read_excel("Data/SIF-S/DataOnly/CMPSchwarzeneger_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "text", "text", "text", "numeric", "numeric", "numeric"))
glimpse(CMPSchwarzeneger_S)

CMPScuds_S <- read_excel("Data/SIF-S/DataOnly/CMPScuds_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))

CMPTunaOfTheFarm_S <- read_excel("Data/SIF-S/DataOnly/CMPTunaOfTheFarm_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))
glimpse(CMPTunaOfTheFarm_S)

CMPZootopia_S <- read_excel("Data/SIF-S/DataOnly/CMPZootopia_S.xlsx", col_types = c("text", "numeric", "numeric", "text", "numeric", "text", "text", "text", "numeric", "numeric"))
```

Next: flag samples with bad readings
"Contained less sulfur than smallest reference"
CMPLiverOfMine: CMP_FISH_291L_S, CMP_FISH_293L_S, CMP_FISH_294L_S

"No Signal"
CMPBuffPants: CMP_FISH_379M_S
 
Fell together:
CMPBuffPants: CMP_FISH_379M_S, CMP_FISH_382M_S

# Merge dataframes
I will address flagging the warning messages of the data after I have merged everything together.
```{r}
RawIsotopeData<-bind_rows(CMPandemic_CN, CMPeas_CN, CMPFish4Ever_CN, CMPFishRFriends_CN, CMPflanzen_CN, CMPhragmites_CN, CMPKrabby_CN, CMPLeftovers_CN, CMPLiverLaVida_CN, CMPLiverLetDie_CN, CMPLiverPool_CN, CMPLiverRoast_CN, CMPLiverWorst_CN, CMPMuscleBob_CN, CMPMuscleStuffin_CN, CMPMysteryMeat_CN, CMPSilenceOThLab_CN, CMPSkrimp_CN, CMPSkrimp2_CN, CMPSmallFry_CN, CMPTheGovernator_CN, CMPVeryStable_CN, CMPZoopSoup_CN, PomVol1_CN, PomVol2_CN, PomVol3_CN, PomVol4_CN, PomVol5_CN, CMPatty_S, CMPBuffPants_S, CMPChoppedLiver_S, CMPeace_S, CMPeachment_S, CMPISeeDeadCMPeople_S, CMPlants_S, CMPlucheae_S, CMPLiverItUp_S, CMPMudBugs_S, CMPLiverGiver_S, CMPLiverLaughLov_S, CMPLiverOfMine_S, CMPMuscleMeat_S, CMPoaceae_S, CMPNotFood_S, CMPSampler_S, CMPSchwarzeneger_S, CMPScuds_S, CMPTunaOfTheFarm_S, CMPZootopia_S)
View(RawIsotopeData)

RawIsotopeData$SampleID <- gsub("_", "-", RawIsotopeData$SampleID)
RawIsotopeData<- separate(RawIsotopeData, col=SampleID, into=c('Project', 'Taxon', 'SpecimenID', 'CNorS', 'Extra'), sep='-', remove= FALSE) #Separates column by '-' and keeps the original column.
unique(RawIsotopeData$Taxon)
RawIsotopeData$Taxon<- gsub('[[:digit:]]+', '', RawIsotopeData$Taxon)
unique(RawIsotopeData$Taxon)
RawIsotopeData$Taxon[RawIsotopeData$Taxon %in% c("Plant", "PlantT", "PlantD", "Detri")] <-"PLANT"
RawIsotopeData$Taxon[RawIsotopeData$Taxon %in% "Zoop"] <-"ZOOP"
RawIsotopeData$Taxon[RawIsotopeData$Taxon %in% "POM"] <-"POM/BA"

write.csv(RawIsotopeData, "Data/RawIsotopeData_05022022.csv")

Raw_CN<- bind_rows(CMPandemic_CN, CMPeas_CN, CMPFish4Ever_CN, CMPFishRFriends_CN, CMPflanzen_CN, CMPhragmites_CN, CMPKrabby_CN, CMPLeftovers_CN, CMPLiverLaVida_CN, CMPLiverLetDie_CN, CMPLiverPool_CN, CMPLiverRoast_CN, CMPLiverWorst_CN, CMPMuscleBob_CN, CMPMuscleStuffin_CN, CMPMysteryMeat_CN, CMPSilenceOThLab_CN, CMPSkrimp_CN, CMPSkrimp2_CN, CMPSmallFry_CN, CMPTheGovernator_CN, CMPVeryStable_CN, CMPZoopSoup_CN, PomVol1_CN, PomVol2_CN, PomVol3_CN, PomVol4_CN, PomVol5_CN)
write.csv(Raw_CN, "Data/Raw_CN_04072022.csv")


Raw_S<- bind_rows(CMPatty_S, CMPBuffPants_S, CMPChoppedLiver_S, CMPeace_S, CMPeachment_S, CMPISeeDeadCMPeople_S, CMPlants_S, CMPlucheae_S, CMPLiverItUp_S, CMPMudBugs_S, CMPLiverGiver_S, CMPLiverLaughLov_S, CMPLiverOfMine_S, CMPMuscleMeat_S, CMPoaceae_S, CMPNotFood_S, CMPSampler_S, CMPSchwarzeneger_S, CMPScuds_S, CMPTunaOfTheFarm_S, CMPZootopia_S)
#To extract taxa, I use this nifty trick below: switching all _ to - (to make it uniform across trays) and then separating by that - and assigning column names

Raw_S$SampleID <- gsub("_", "-", Raw_S$SampleID)
Raw_S<- separate(Raw_S, col=SampleID, into=c('Project', 'Taxon', 'SpecimenID', 'CNorS', 'Extra'), sep='-', remove= FALSE)
Raw_S$Taxon<- gsub('[[:digit:]]+', '', Raw_S$Taxon)
unique(Raw_S$Taxon)
Raw_S$Taxon[Raw_S$Taxon %in% c("Plant", "PlantT", "PlantD", "Detri")] <-"PLANT"
Raw_S$Taxon[Raw_S$Taxon %in% "Zoop"] <-"ZOOP"

write.csv(Raw_S, "Data/Raw_S_05022022.csv")

#Manually added taxon columns, so read-in the excel versions of the raw data with taxon columns
RawIsotopeData_05022022 <- read_excel("Data/RawIsotopeData_05022022.xlsx")

Raw_S_05022022<- read_excel("Data/Raw_S_05022022.xlsx")


Raw_CN_04072022 <- read_excel("Data/Raw_CN_04072022.xlsx")

```

# Now I want to attach sample information (species ID, site, etc) to this table.

## Joining fish data to SIF data
```{r}
#okay so I forgot I have to do each taxonomic group separately because of the different naming techniques...
#So let's pull all the rows of fish out first and foremost

FishIsotopeData_CN<- Raw_CN_04072022 %>% filter(Taxon == "FISH")

FishIsotopeData_S<- Raw_S_05022022 %>% filter(Taxon == "FISH")


FishIsotopeData_CN$Fish_Number<- regmatches(FishIsotopeData_CN$SampleID, gregexpr("[[:digit:]]+", FishIsotopeData_CN$SampleID)) #makes a list.

FishIsotopeData_CN$Fish_Number<-as.numeric(FishIsotopeData_CN$Fish_Number)

FishIsotopeData_S$Fish_Number<- regmatches(FishIsotopeData_S$SampleID, gregexpr("[[:digit:]]+", FishIsotopeData_S$SampleID)) #makes a list.

FishIsotopeData_S$Fish_Number<-as.numeric(FishIsotopeData_S$Fish_Number)

#I need a column with retains the M or L.

FishIsotopeData_S$SampleID <- gsub("_", "-", FishIsotopeData_S$SampleID)

FishIsotopeData_S_SampleIDs<- separate(FishIsotopeData_S, col=SampleID, into=c('Project', 'Taxa', 'FishSpecimenID', 'CNorS'), sep='-')
View(FishIsotopeData_S_SampleIDs)


FishIsotopeData_CN$SampleID <- gsub("_", "-", FishIsotopeData_CN$SampleID)

FishIsotopeData_CN_SampleIDs<- separate(FishIsotopeData_CN, col=SampleID, into=c('Project', 'Taxa', 'FishSpecimenID', 'CNorS'), sep='-')
View(FishIsotopeData_CN_SampleIDs)

#Now join the S and CN data so that each fish has 1 row for muscle and 1 row for liver.

FishIsotopeData_Simple<-merge(FishIsotopeData_S_SampleIDs, FishIsotopeData_CN_SampleIDs, by= "FishSpecimenID") %>% select(-ends_with(".y"))

View(FishIsotopeData_Simple)
colnames(FishIsotopeData_Simple)


#Okay, now I want to attach the metadata.

names(FishIsotopeData_Simple)[names(FishIsotopeData_Simple)=="Fish_Number.x"]<- "Fish_Number"

FishIsotopeAndMetaData<- merge(FishIsotopeData_Simple, FishInfo_040122, by= "Fish_Number")
View(FishIsotopeAndMetaData) #GOT IT

#Remove Pilot fish and WL-Out... 
FishIsotopeAndMetaData<- FishIsotopeAndMetaData[!(FishIsotopeAndMetaData$Site == "WL-O"),]
unique(FishIsotopeAndMetaData$Site) #done

#Remove fish from pilot study
FishIsotopeAndMetaData<- FishIsotopeAndMetaData[!(FishIsotopeAndMetaData$Season == "Pilot"),]
unique(FishIsotopeAndMetaData$Season)

#Fix spelling errors
unique(FishIsotopeAndMetaData$`Age Class`) #"Age 1+" & "age 1+", "adult" & "Adult"    
FishIsotopeAndMetaData$`Age Class`<- as.character(FishIsotopeAndMetaData$`Age Class`)
FishIsotopeAndMetaData$`Age Class`[FishIsotopeAndMetaData$`Age Class` == "age 1+"] <-"Age 1+"
unique(FishIsotopeAndMetaData$`Age Class`)

FishIsotopeAndMetaData$`Age Class`[FishIsotopeAndMetaData$`Age Class` == "adult"] <-"Adult"

FishIsotopeAndMetaData$`Age Class`[FishIsotopeAndMetaData$`Age Class` == "juvenile"] <-"Juvenile"
unique(FishIsotopeAndMetaData$`Age Class`)

#Need to split up muscle and liver data.

FishMuscleData<- FishIsotopeAndMetaData[!(FishIsotopeAndMetaData$Type_of_Material == "Liver"),]
unique(FishMuscleData$Type_of_Material)

FishLiverData<- FishIsotopeAndMetaData[!(FishIsotopeAndMetaData$Type_of_Material == "Muscle"),]

FishLiverData.<- FishLiverData[!(FishLiverData$Type_of_Material == "Muscle Tissue"),] 
unique(FishLiverData.$Type_of_Material)

View(FishMuscleData)

#Save!

write.csv(FishMuscleData, "Data/FishMuscleData_050222.csv")

write.csv(FishLiverData., "Data/FishLiverData_050222.csv")
```

## Let's do plants next.
```{r}
PlantIsotopeData_CN<- Raw_CN_04072022 %>% filter(Taxon == "PLANT")
#Okay now I need to create an ID column to merge this dataset with sulfur. 
PlantIsotopeData_CN$SampleID<-gsub("_", "-", PlantIsotopeData_CN$SampleID) #Making the dashes the same throughout each tray.
PlantIsotopeData_Specimens_CN<- separate(PlantIsotopeData_CN, col=SampleID, into=c('Project', 'SpecimenID', 'Trial', 'CNorS'), sep='-') #Separating out the SampleID column into its pieces
PlantIsotopeData_SpecimenID_CN<- PlantIsotopeData_Specimens_CN %>% unite("SampleID", c("SpecimenID","Trial"), sep="_", remove=FALSE) #Uniting the sample ID and Trial so that I don't lose trial information and freak out r.

#Now I repeat above steps with sulfur data.
PlantIsotopeData_S<- Raw_S_05022022 %>% filter(Taxon == "PLANT")
PlantIsotopeData_S$SampleID<-gsub("_", "-", PlantIsotopeData_S$SampleID) #Making the dashes the same throughout each tray.
PlantIsotopeData_Specimens_S<- separate(PlantIsotopeData_S, col=SampleID, into=c('Project', 'SpecimenID', 'Trial', 'CNorS'), sep='-') #Separating out the SampleID column into its pieces
PlantIsotopeData_SpecimenID_S<- PlantIsotopeData_Specimens_S %>% unite("SampleID", c("SpecimenID","Trial"), sep="_", remove=FALSE)

PlantIsotopeData_Simple<-merge(PlantIsotopeData_SpecimenID_S, PlantIsotopeData_SpecimenID_CN, by= "SampleID") %>% select(-ends_with(".y"))
#Create a column that can merge with plant metadata
PlantIsotopeData_Simple$PlantID<- sub('Plant', '', PlantIsotopeData_Simple$SpecimenID.x)

#Okay, now I want to attach the metadata.
names(PlantInfo_121721)[names(PlantInfo_121721) == "Sample_ID"] <- "PlantID"


PlantInfo_121721$SpecimenID<-PlantInfo_121721$Sample_ID
View(PlantInfo_121721)

#NOW we merge.
PlantIsotopeAndMetadata<- merge(PlantIsotopeData_Simple, PlantInfo_121721, by="PlantID")
View(PlantIsotopeAndMetadata)

unique(PlantIsotopeAndMetadata$SpeciesCode)

PlantIsotopeAndMetadata$Class[PlantIsotopeAndMetadata$SpeciesCode %in% c("SAGO", "MYSP", "FILA")]<- "SAV"

PlantIsotopeAndMetadata$Class[PlantIsotopeAndMetadata$SpeciesCode %in% c("PHAU", "TYAN", "SCAC", "SCAM", "SCCA")]<- "EV"

PlantIsotopeAndMetadata$Class[PlantIsotopeAndMetadata$SpeciesCode %in% c("ARSU", "SAPA", "CASE", "JACA", "LELA", "ROCA", "LAJE", "JUBA", "LOCO", "PLOD")]<- "Terrestrial"

PlantIsotopeAndMetadata$Class[PlantIsotopeAndMetadata$SpeciesCode %in% c("LEMNA", "AZFI")]<- "Floating Veg"

PlantIsotopeAndMetadata$Class[PlantIsotopeAndMetadata$SpeciesCode %in% "DET"]<- "Det"

#Need a column with species info
PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "SAGO"]<- "SAGO"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "MYSP"]<- "Myriophyllum spicatum"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "FILA"]<- "Filamentous algae"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "PHAU"]<- "Phragmites australis"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "TYAN"]<- "Typha angustifolia"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "SCAC"]<- "Schoenoplectus acutusa"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "SCAM"]<- "Schoenoplectus americanus"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "SCCA"]<- "Schoenoplectus californicus"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "ARSU"]<- "Sarcocornia/Salicornia pacifica" #ARSU is outdated...

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "SAPA"]<- "Sarcocornia/Salicornia pacifica"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "CASE"]<- "Calystegia sepium"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "JACA"]<- "Jaumea carnosa"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "LELA"]<- "Lepidium latifolium"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "ROCA"]<- "Rosa californica"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "LAJE"]<- "Lathyrus jepsonii jepsonii"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "JUBA"]<- "Juncus balticus"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "LOCO"]<- "Lotus corniculatus"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "PLOD"]<- "Pluchea odorata"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "LEMNA"]<- "Lemna sp"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "AZFI"]<- "Azolla"

PlantIsotopeAndMetadata$Species[PlantIsotopeAndMetadata$SpeciesCode %in% "DET"]<- "Det"

unique(PlantIsotopeAndMetadata$Species)

#SAVE IT
write.csv(PlantIsotopeAndMetadata, "Data/PlantIsotopeAndMetaData_050222.csv")
```

## Now zoops
```{r}
ZoopIsotopeData<- RawIsotopeData_05022022 %>% filter(Taxon == "ZOOP")

ZoopIsotopeData_Vials<- separate(ZoopIsotopeData, col=SampleID, into=c('Project', 'Zooplankton', 'Vial', 'CNorS'), sep='-') 

ZoopIsotopeAndMetadata<-merge(ZoopIsotopeData_Vials, ZoopInfo, by="Vial")

#Problem: Merging by vial gives issues because each sample has a unique vial name. What I really want to combine by is the SampleID minus the CN or S information. So somehow need to remove that info from the string...
ZoopIsotopeAndMetadata<- ZoopIsotopeAndMetadata %>% unite("SampleID", c("ZoopSpecies","CollectionDate", "Site"), sep="_", remove=FALSE) #Cool, I've created a column to sort this out.
#This seems silly but I think it will work. I am going to separate this df into 2 (one for CN and one for S) and then merge them back together based upon the newly created SampleID.
ZoopIsotopeAndMetadata_CN<- ZoopIsotopeAndMetadata %>% filter(CNorS == "CN")
ZoopIsotopeAndMetadata_S<- ZoopIsotopeAndMetadata %>% filter(CNorS == "S")
#Delete problem columns
ZoopIsotopeAndMetadata_CN_Clean<- ZoopIsotopeAndMetadata_CN %>% subset(select= -c(CNorS, SpecimenID, Vial, Well_Id, Analysis, AnalysisNumber, MassSpec, PlantNumber, Treatment, Notes, `SampleWeight(mg)fromSampleList`, `SampleWeight(mg)`, Internal_ID, `TinWeight(g)`, `FullDryWeight(g)`, SampleComposition, ApproxCount, Extra, TrayName, Initials))

ZoopIsotopeAndMetadata_S_Clean<- ZoopIsotopeAndMetadata_S %>% subset(select= -c(CNorS, SpecimenID, Vial, Well_Id, Analysis, AnalysisNumber, MassSpec, PlantNumber, Treatment, Notes, `SampleWeight(mg)fromSampleList`, `SampleWeight(mg)`, Internal_ID, `TinWeight(g)`, `FullDryWeight(g)`, SampleComposition, ApproxCount, Extra, TrayName, Initials))
ZoopIsotopeAndMetadata_Clean<-merge(ZoopIsotopeAndMetadata_CN_Clean, ZoopIsotopeAndMetadata_S_Clean, by="SampleID")
ZoopIsotopeAndMetadata_Cleaned<- ZoopIsotopeAndMetadata_Clean %>% subset(select=-c(`D34SVCDT(permill).x`, `TotalS(ug).x`, S_Comment.x, `D34S_MeanReferenceSD_plusminus(permill).x`, `D34S_MeanAbsAccuracy_plusminus(permill).x`, `D13CVPDB(permill).y`, `D13C_MeanReferenceSD_plusminus(permill).y`, `D13C_MeanAbsAccuracy_plusminus(permill).y`, C_Comment.y, `D15N_MeanAbsAccuracy_plusminus(permill).y`, `D15N_MeanReferenceSD_plusminus(permill).y`, `D15N_MeanAbsAccuracy_plusminus(permill).y`, NComment.y, Type_of_Material.y, Site.y, CollectionDate.y, Season.y, ZoopSpecies.y, `QAQC'd?.y`, Project.y, Zooplankton.y, Taxon.y, `TotalC(ug).y`, `TotalN(ug).y`))

#Can't figure out how to clean the column names to remove .x and .y so I will do it manually in excel...

write.csv(ZoopIsotopeAndMetadata_Cleaned, "Data/ZoopIsotopeAndMetaData_050222.csv")
```

## Now Pom and BA
Note: No sulfur data available.
```{r}
#ID row for POM and BA were the same. I went through and manually changed BA samples to POM based on Alice's masterfile and the assumption that BA was submitted later than POM.
IsotopeData_POMEdited_04052022 <- read_excel("Data/IsotopeData_POMEdited_04052022.xlsx")

POM_BENTHIC_Info_edited_040522 <- read_excel("Data/POM_BENTHIC_Info_edited_040522.xlsx")

library(dplyr)

POMBAIsotopeData<- IsotopeData_POMEdited_04052022 %>% filter(Taxon == "POM/BA")
View(POMBAIsotopeData)

# Rename column 
names(POMBAIsotopeData)[names(POMBAIsotopeData) == "SampleID"] <- "CarolinesLabel"

POM_BENTHIC_Info_edited_040522$CarolinesLabel <- gsub("_", "-", POM_BENTHIC_Info_edited_040522$CarolinesLabel) #Changes all the underscores to hyphens to match sif data.
POM_BA_IsotopeAndMetadata<-merge(POM_BENTHIC_Info_edited_040522, POMBAIsotopeData, by="CarolinesLabel")
View(POM_BA_IsotopeAndMetadata)

#Fixing spelling errors
POM_BA_IsotopeAndMetadata$Site[POM_BA_IsotopeAndMetadata$Site == "PT3"] <-"PT"

POM_BA_IsotopeAndMetadata$Site[POM_BA_IsotopeAndMetadata$Site == "unknown"] <-"NA"

POM_BA_IsotopeAndMetadata$`D13CVPDB(permill)`<- as.numeric(POM_BA_IsotopeAndMetadata$`D13CVPDB(permill)`)

POM_BA_IsotopeAndMetadata$`D15NAir(permill)`<- as.numeric(POM_BA_IsotopeAndMetadata$`D15NAir(permill)`)

POM_BA_IsotopeAndMetadata$`D34SVCDT(permill)`<- as.numeric(POM_BA_IsotopeAndMetadata$`D34SVCDT(permill)`)

write.csv(POM_BA_IsotopeAndMetadata, "Data/POM_BA_IsotopeAndMetaData_040522.csv")

```

#Last but not least, inverts.
```{r}
InvertIsotopeData_CN<- Raw_CN_04072022 %>% filter(Taxon == "INVERT")
#Okay now I need to create an ID column to merge this dataset with sulfur. 
InvertIsotopeData_CN$SampleID<-gsub("_", "-", InvertIsotopeData_CN$SampleID) #Making the dashes the same throughout each tray.
InvertIsotopeData_Specimens_CN<- separate(InvertIsotopeData_CN, col=SampleID, into=c('Project', 'Invertebrate', 'SpecimenID', 'Trial'), sep='-') #Separating out the SampleID column into its pieces 
#NOTE: Trial column is CN or S for ones without trial numbers. 
#InvertIsotopeData_CN<- InvertIsotopeData_CN %>% unite("SampleID", c("SpecimenID","Trial"), sep="_", remove=FALSE) #Uniting the sample ID and Trial so that I don't lose trial information and freak out r.

#Now I repeat above steps with sulfur data.
InvertIsotopeData_S<- Raw_S_05022022 %>% filter(Taxon == "INVERT")
InvertIsotopeData_S$SampleID<-gsub("_", "-", InvertIsotopeData_S$SampleID) #Making the dashes the same throughout each tray.
InvertIsotopeData_Specimens_S<- separate(InvertIsotopeData_S, col=SampleID, into=c('Project', 'Invertebrate', 'SpecimenID', 'Trial'), sep='-')

InvertIsotopeData_Simple<-merge(InvertIsotopeData_Specimens_S, InvertIsotopeData_Specimens_CN, by= "SpecimenID") %>% select(-ends_with(".y"))

#Need to delete hyphen from sample ID in the LargeMacroinvert df
LargeMacroinvetInfo_040322$Sample_ID<-gsub("-", "", LargeMacroinvetInfo_040322$Sample_ID)

names(LargeMacroinvetInfo_040322)[names(LargeMacroinvetInfo_040322) == "Sample_ID"] <- "SpecimenID" #rename

LargeMacroinvert_IsotopeAndMetadata<- merge(LargeMacroinvetInfo_040322, InvertIsotopeData_Simple, by="SpecimenID")

#Introduce Season column
LargeMacroinvert_IsotopeAndMetadata$Collection_Date<-mdy(LargeMacroinvert_IsotopeAndMetadata$Collection_Date)

str(LargeMacroinvert_IsotopeAndMetadata$Collection_Date)

LargeMacroinvert_IsotopeAndMetadata$Month<- format(LargeMacroinvert_IsotopeAndMetadata$Collection_Date, format = "%m")
unique(LargeMacroinvert_IsotopeAndMetadata$Month)

LargeMacroinvert_IsotopeAndMetadata$Season[LargeMacroinvert_IsotopeAndMetadata$Month %in% "06"]<-"Summer"
LargeMacroinvert_IsotopeAndMetadata$Season[LargeMacroinvert_IsotopeAndMetadata$Month %in% "07"]<-"Summer"
LargeMacroinvert_IsotopeAndMetadata$Season[LargeMacroinvert_IsotopeAndMetadata$Month %in% "08"]<-"Fall"
LargeMacroinvert_IsotopeAndMetadata$Season[LargeMacroinvert_IsotopeAndMetadata$Month %in% "09"]<-"Fall"
#Make site names match (SB = FM)
unique(LargeMacroinvert_IsotopeAndMetadata$Site)
LargeMacroinvert_IsotopeAndMetadata$Site[LargeMacroinvert_IsotopeAndMetadata$Site %in% "SB"]<-"FM"

#SAVE
write.csv(LargeMacroinvert_IsotopeAndMetadata, "Data/LargeMacroinvert_IsotopeAndMetaData_050222.csv")

#Okay, now small macroinverts
names(CMP_SmallMacroinvertInfo_04022022)[names(CMP_SmallMacroinvertInfo_04022022) == "SampleID_Simple"] <- "SpecimenID" #rename

SmallMacroinvert_IsotopeAndMetadata<- merge(InvertIsotopeData_Simple, CMP_SmallMacroinvertInfo_04022022, by="SpecimenID")%>% select(-ends_with(".y"))
#SAVE
write.csv(SmallMacroinvert_IsotopeAndMetadata, "Data/SmallMacroinvert_IsotopeAndMetaData_050222.csv")
```