---
title: "Plotting with Sulfur"
author: "Caroline Newell"
date: '2022-04-28'
output: html_document
editor_options: 
  chunk_output_type: console
---
From Dr. Elliot Arnold: "Please note that some samples were below our LOQ of 15ug or 5ug for our Sercon and Elementar machines, respectively. You could probably push the lower limit of quantification to 10ugS for the Sercon results, but I would exclude all samples below that."
So I will look out outliers of sulfur and remove those with below 10 ugS.

 
##Load packages
```{r}
library(readxl)
library(lubridate)
library(viridis)
library(RColorBrewer)
library(ggpubr)
library(ggsci)
library(tidyverse)
standard_error <- function(x) sd(x) / sqrt(length(x)) # Create own function
```

#Read in data
```{r}
FishMuscleData_050222 <- read_excel("Data/FishMuscleData_050222.xlsx")
FishLiverData_050222 <- read_excel("Data/FishLiverData_050222.xlsx")
SmallMacroinvert_IsotopeAndMetaData_050222 <- read_excel("Data/SmallMacroinvert_IsotopeAndMetaData_050222.xlsx")
LargeMacroinvert_IsotopeAndMetaData_050222 <- read_excel("Data/LargeMacroinvert_IsotopeAndMetaData_050222.xlsx")
PlantIsotopeAndMetaData_050222 <- read_excel("Data/PlantIsotopeAndMetaData_050222.xlsx")
ZoopIsotopeAndMetaData_050222 <- read_excel("Data/ZoopIsotopeAndMetaData_050222.xlsx")
POM_BA_IsotopeAndMetaData_042522 <- read_excel("Data/POM_BA_IsotopeAndMetaData_042522.xlsx") #NO SULFUR DATA FOR POM/BA
```

#Sulfur vs Carbon Plots
## Fish Muscle

###Look for bad data
```{r}
#Sulfur
unique(FishMuscleData_050222$S_Comment)

FishMuscleData_050222_NoOutliers<-FishMuscleData_050222 %>% filter(!S_Comment %in% c("No signal", "H5 and H6 fell in together"))

unique(FishMuscleData_050222_NoOutliers$S_Comment)

#Carbon
unique(FishMuscleData_050222_NoOutliers$C_Comment)
FishMuscleData_050222_NoOutliers<- FishMuscleData_050222_NoOutliers %>% filter(!C_Comment == "H3-H6 could be mixed up")
```

```{r}
colnames(FishMuscleData_050222_NoOutliers)
FishMuscleData_050222_NoOutliers$`D34SVCDT(permill)`<-as.numeric(FishMuscleData_050222_NoOutliers$`D34SVCDT(permill)`)
str(FishMuscleData_050222_NoOutliers)
FishMuscles_MeansSd<-FishMuscleData_050222_NoOutliers%>% 
  group_by(Species, Site, Season, `Age Class`) %>% 
  summarize(n=n(),
            alpha = 0.05,
            D13C_mean = sum(`D13CVPDB(permill)`/n, na.rm=TRUE), 
            D13C_SD = sqrt(sum((`D13CVPDB(permill)`- (D13C_mean))^2)/(n-1)),
            D13C_StdError= standard_error(`D13CVPDB(permill)`),
            D15N_mean = sum(`D15NAir(permill)`/n, na.rm=TRUE),
            D15N_SD = sqrt(sum((`D15NAir(permill)`- (D15N_mean))^2)/(n-1)),
            D15N_StdError= standard_error(`D15NAir(permill)`),
            D35S_mean = sum(`D34SVCDT(permill)`/n, na.rm=TRUE),
            D35S_SD = sqrt(sum((`D34SVCDT(permill)`- (D35S_mean))^2)/(n-1)),
            D35S_StdError= standard_error(`D34SVCDT(permill)`)
            )

FishMuscles_MeansSd$D13C_StdError[is.nan(FishMuscles_MeansSd$D13C_StdError)]<-0

FishMuscles_MeansSd$D13C_StdError[is.na(FishMuscles_MeansSd$D13C_StdError)]<-0

FishMuscles_MeansSd$D13C_SD[is.nan(FishMuscles_MeansSd$D13C_SD)]<-0

FishMuscles_MeansSd$D15N_StdError[is.na(FishMuscles_MeansSd$D15N_StdError)]<-0

FishMuscles_MeansSd$D15N_SD[is.nan(FishMuscles_MeansSd$D15N_SD)]<-0

FishMuscles_MeansSd$D35S_StdError[is.na(FishMuscles_MeansSd$D35S_StdError)]<-0

FishMuscles_MeansSd$D35S_SD[is.nan(FishMuscles_MeansSd$D35S_SD)]<-0
```


###Plot S vs C
```{r}
FishMuscles_MeansSd.fall<- FishMuscles_MeansSd %>% filter(Season == "Fall")
unique(FishMuscles_MeansSd.fall$Species)

FishMuscles_MeansSd.summer<- FishMuscles_MeansSd %>% filter(Season == "Summer")
unique(FishMuscles_MeansSd.summer$Species)

FishMuscleData_SpeciesBothSeasons<- FishMuscles_MeansSd %>% filter(Species %in% c("BC", "SCP", "ST",  "TP",  "SB",  "YFG", "SKG", "SG"))

FishMusclePlot<-FishMuscleData_SpeciesBothSeasons %>% ggplot(aes(D13C_mean, D35S_mean, color= Site)) + 
  geom_point(aes(color = Site, shape=Species), size=3) + 
  scale_shape_manual(values=rep(0:15, 1))+
  labs(title = "Muscle Means And Standard Error Fish Caught Both Seasons") +
  theme_bw()+ 
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) + 
  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
FishMusclePlot
```

## Fish Liver
###Look for bad data
```{r}
#Sulfur
#I'm just going to remove sample loss fish and fish below LOQ that had below 10 ug because Dr. Arnold said it was okay.
FishLiverData_050222$`TotalS(ug)`<- as.numeric(FishLiverData_050222$`TotalS(ug)`)
FishLiverData_050222_NoOutliers<-FishLiverData_050222 %>% filter(!`TotalS(ug)`<10, !S_Comment == "sample loss")

unique(FishLiverData_050222_NoOutliers$S_Comment)

#Carbon
unique(FishLiverData_050222_NoOutliers$C_Comment) #lovely.
```

### Summarize
```{r}
FishLiverData_050222_NoOutliers$`D34SVCDT(permill)`<-as.numeric(FishLiverData_050222_NoOutliers$`D34SVCDT(permill)`)
str(FishLiverData_050222_NoOutliers)

FishLivers_MeansSd<-FishLiverData_050222_NoOutliers%>% 
  group_by(Species, Site, Season, `Age Class`) %>% 
  summarize(n=n(),
            alpha = 0.05,
            D13C_mean = sum(`D13CVPDB(permill)`/n, na.rm=TRUE), 
            D13C_SD = sqrt(sum((`D13CVPDB(permill)`- (D13C_mean))^2)/(n-1)),
            D13C_StdError= standard_error(`D13CVPDB(permill)`),
            D15N_mean = sum(`D15NAir(permill)`/n, na.rm=TRUE),
            D15N_SD = sqrt(sum((`D15NAir(permill)`- (D15N_mean))^2)/(n-1)),
            D15N_StdError= standard_error(`D15NAir(permill)`),
            D35S_mean = sum(`D34SVCDT(permill)`/n, na.rm=TRUE),
            D35S_SD = sqrt(sum((`D34SVCDT(permill)`- (D35S_mean))^2)/(n-1)),
            D35S_StdError= standard_error(`D34SVCDT(permill)`)
            )

FishLivers_MeansSd$D13C_StdError[is.nan(FishLivers_MeansSd$D13C_StdError)]<-0

FishLivers_MeansSd$D13C_StdError[is.na(FishLivers_MeansSd$D13C_StdError)]<-0

FishLivers_MeansSd$D13C_SD[is.nan(FishLivers_MeansSd$D13C_SD)]<-0

FishLivers_MeansSd$D15N_StdError[is.na(FishLivers_MeansSd$D15N_StdError)]<-0

FishLivers_MeansSd$D15N_SD[is.nan(FishLivers_MeansSd$D15N_SD)]<-0

FishLivers_MeansSd$D35S_StdError[is.na(FishLivers_MeansSd$D35S_StdError)]<-0

FishLivers_MeansSd$D35S_SD[is.nan(FishLivers_MeansSd$D35S_SD)]<-0
```

### Plot S vs C
```{r}
FishLivers_MeansSd.Fall<- FishLivers_MeansSd %>% filter(Season == "Fall")
unique(FishLivers_MeansSd.Fall$Species)

FishLivers_MeansSd.Summer<- FishLivers_MeansSd %>% filter(Season == "Summer")
unique(FishLivers_MeansSd.Summer$Species)

FishLiverData_SpeciesBothSeasons<- FishLivers_MeansSd %>% filter(Species %in% c("BC", "SB",  "ST",  "YFG", "SG",  "SCP", "SKG", "TP"))

FishLiverPlot<-FishLiverData_SpeciesBothSeasons %>% ggplot(aes(D13C_mean, D35S_mean, color= Site)) + 
  geom_point(aes(color = Site, shape=Species), size=3) + 
  scale_shape_manual(values=rep(0:15, 1))+
  labs(title = "Liver Means And Standard Error Fish Caught Both Seasons") +
  theme_bw()+ 
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) + 
  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
FishLiverPlot
```

## Inverts
###Cleaning
```{r}
#Remove rows with combustion column failure
unique(SmallMacroinvert_IsotopeAndMetaData_050222$C_Comment)
SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved<- SmallMacroinvert_IsotopeAndMetaData_050222 %>% filter(NComment %in% "NA")
unique(SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$C_Comment)
#Cool

unique(SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$S_Comment)
SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$`TotalS(ug)`<- as.numeric(SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$`TotalS(ug)`)
SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved<- SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved %>% filter(!`TotalS(ug)`<10)

#Remove rows with combustion column failure
unique(LargeMacroinvert_IsotopeAndMetaData_050222$C_Comment)
LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved<- LargeMacroinvert_IsotopeAndMetaData_050222 %>% filter(NComment %in% c("Remaining samples moved to another run", "NA"))
unique(LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$C_Comment)
#Cool

unique(LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved$S_Comment)

LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved<- LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved %>% filter(S_Comment %in% "NA")
```
### Combining
```{r}
LargeMacs<- LargeMacroinvert_IsotopeAndMetaData_BadCommentsRemoved %>% subset(select =c("SpecimenID", "Species", "Site", "Season", "D13CVPDB(permill)", "D15NAir(permill)", "D34SVCDT(permill)" ))
SmallMacs<-SmallMacroinvert_IsotopeAndMetaData_BadCommentsRemoved %>% subset(select =c("SpecimenID", "Species", "Site", "Season", "D13CVPDB(permill)", "D15NAir(permill)", "D34SVCDT(permill)" ))

Inverts<- rbind(LargeMacs, SmallMacs)
Inverts$Species[Inverts$Species == "Harris Mud Crab"] <-"Harris mud crab"
```

### Summarizing
```{r}
Inverts$`D34SVCDT(permill)`<-as.numeric(Inverts$`D34SVCDT(permill)`)

Inverts$`D15NAir(permill)`<-as.numeric(Inverts$`D15NAir(permill)`)

Inverts$`D13CVPDB(permill)`<-as.numeric(Inverts$`D13CVPDB(permill)`)

str(Inverts$`D13CVPDB(permill)`)

Inverts_MeansSd<-Inverts%>% 
  group_by(Species, Site, Season) %>% 
  summarize(n=n(),
            alpha = 0.05,
            D13C_mean = sum(`D13CVPDB(permill)`/n, na.rm=TRUE), 
            D13C_SD = sqrt(sum((`D13CVPDB(permill)`- (D13C_mean))^2)/(n-1)),
            D13C_StdError= standard_error(`D13CVPDB(permill)`),
            D15N_mean = sum(`D15NAir(permill)`/n, na.rm=TRUE),
            D15N_SD = sqrt(sum((`D15NAir(permill)`- (D15N_mean))^2)/(n-1)),
            D15N_StdError= standard_error(`D15NAir(permill)`),
            D35S_mean = sum(`D34SVCDT(permill)`/n, na.rm=TRUE),
            D35S_SD = sqrt(sum((`D34SVCDT(permill)`- (D35S_mean))^2)/(n-1)),
            D35S_StdError= standard_error(`D34SVCDT(permill)`)
            )

Inverts_MeansSd$D13C_StdError[is.nan(Inverts_MeansSd$D13C_StdError)]<-0

Inverts_MeansSd$D13C_StdError[is.na(Inverts_MeansSd$D13C_StdError)]<-0

Inverts_MeansSd$D13C_SD[is.nan(Inverts_MeansSd$D13C_SD)]<-0

Inverts_MeansSd$D15N_StdError[is.na(Inverts_MeansSd$D15N_StdError)]<-0

Inverts_MeansSd$D15N_SD[is.nan(Inverts_MeansSd$D15N_SD)]<-0

Inverts_MeansSd$D35S_StdError[is.na(Inverts_MeansSd$D35S_StdError)]<-0

Inverts_MeansSd$D35S_SD[is.nan(Inverts_MeansSd$D35S_SD)]<-0
```

###Plot S v C
```{r}
#Which species caught both seasons?
Inverts_MeansSd_Fall<- Inverts_MeansSd %>% filter(Season == "Fall")
unique(Inverts_MeansSd_Fall$Species)

Inverts_MeansSd_Summer<- Inverts_MeansSd %>% filter(Season == "Summer")
unique(Inverts_MeansSd_Summer$Species)

Inverts_MeansSd_BothSeasons<- Inverts_MeansSd %>% filter(Species %in% c("Corbicula", "Crab Zoea", "Exopalaemon", "Harris mud crab", "Maeotias", "Red swamp crayfish"))

InvertPlot<-Inverts_MeansSd_BothSeasons %>% ggplot(aes(D13C_mean, D35S_mean, color= Site)) + 
  geom_point(aes(color = Site, shape=Species), size=3) + 
  scale_shape_manual(values=rep(0:15, 1))+
  labs(title = "Invert Means And Standard Error Both Seasons") +
  theme_bw()+ 
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) + 
  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
InvertPlot
```
## Zoops
###Removing rows with warnings from sif
```{r}
#Remove rows with combustion column failure
unique(ZoopIsotopeAndMetaData_050222$C_Comment)
#Cool

unique(ZoopIsotopeAndMetaData_050222$S_Comment)

ZoopIsotopeAndMetaData_050222$`TotalS(ug)`<- as.numeric(ZoopIsotopeAndMetaData_050222$`TotalS(ug)`)

Zoops_IsotopeAndMetaData_BadCommentsRemoved<- ZoopIsotopeAndMetaData_050222 %>% filter(!`TotalS(ug)`<10, !S_Comment %in% "Run Error, sample too large, possible salt contamination")
```

### Summarize
Actually, I don't need to summarize this because there is only one sample each - no mean or sd available. So will just make sure r knows the values are numeric.
```{r}
Zoops_IsotopeAndMetaData_BadCommentsRemoved<- Zoops_IsotopeAndMetaData_BadCommentsRemoved %>% subset(select=-`D15NAir(permill)...21`)

Zoops_IsotopeAndMetaData_BadCommentsRemoved<-Zoops_IsotopeAndMetaData_BadCommentsRemoved %>% 
  rename(`D15NAir(permill)` = `D15NAir(permill)...8`)

Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D34SVCDT(permill)`<-as.numeric(Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D34SVCDT(permill)`)

Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D15NAir(permill)`<-as.numeric(Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D15NAir(permill)`)

Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D13CVPDB(permill)`<-as.numeric(Zoops_IsotopeAndMetaData_BadCommentsRemoved$`D13CVPDB(permill)`)
```

### Plot S vs C
```{r}
#Fixing spelling mistakes
Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies[Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies %in% c("500 um", ">500 um", "500um")] <-">500 um"

Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies[Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies %in% c("200um", "200-500 um")] <-"200-500 um"

#Which of the species have data for both seasons?
ZoopsFall<- Zoops_IsotopeAndMetaData_BadCommentsRemoved %>% filter(Season=="Fall")
unique(ZoopsFall$ZoopSpecies)

ZoopsSum<- Zoops_IsotopeAndMetaData_BadCommentsRemoved %>% filter(Season=="Summer")
unique(ZoopsSum$ZoopSpecies)

Zoops_SpeciesBothSeasons<- Zoops_IsotopeAndMetaData_BadCommentsRemoved %>% filter(ZoopSpecies %in% c( ">500 um", "200-500 um", "100 um", "A. sinensis", "P. forbesi")) #Not actually removing anything...

Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies<- factor(Zoops_IsotopeAndMetaData_BadCommentsRemoved$ZoopSpecies, levels = c(">500 um", "200-500 um", "100 um", "A. sinensis", "P. forbesi")) #Changing level order 

#Plot
ZoopsPlot<-Zoops_SpeciesBothSeasons %>% ggplot(aes(`D13CVPDB(permill)`, `D34SVCDT(permill)`, color= Site)) + 
  geom_point(aes(color = Site, shape=ZoopSpecies), size=5) + 
  scale_shape_manual(values=rep(0:15, 1))+
  labs(title = "Zooplankton Values Both Seasons") +
  theme_bw()+ 
  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
ZoopsPlot
```

## Plants
###Removing rows with warnings from sif
```{r}
#Remove rows with combustion column failure
unique(PlantIsotopeAndMetaData_050222$C_Comment)
#Cool

unique(PlantIsotopeAndMetaData_050222$S_Comment)
PlantIsotopeAndMetaData_050222$`TotalS(ug)`<- as.numeric(PlantIsotopeAndMetaData_050222$`TotalS(ug)`)
Plant_IsotopeAndMetaData_BadCommentsRemoved<- PlantIsotopeAndMetaData_050222 %>% filter(!`TotalS(ug)`<10)
```

### Summarize
```{r}
Plant_IsotopeAndMetaData_BadCommentsRemoved.Fall<- Plant_IsotopeAndMetaData_BadCommentsRemoved %>% filter(Season=="Fall")
unique(Plant_IsotopeAndMetaData_BadCommentsRemoved.Fall$Species)

Plant_IsotopeAndMetaData_BadCommentsRemoved.Summer<- Plant_IsotopeAndMetaData_BadCommentsRemoved %>% filter(Season=="Summer")
unique(Plant_IsotopeAndMetaData_BadCommentsRemoved.Summer$Species)

Plants_SpeciesBothSeasons<- Plant_IsotopeAndMetaData_BadCommentsRemoved %>% filter(Species %in% c("Phragmites australis", "Calystegia sepium","Myriophyllum spicatum","Schoenoplectus acutusa","Schoenoplectus americanus","Filamentous algae","Typha angustifolia","SAGO","Sarcocornia/Salicornia pacifica","Det"), !Season %in% "NA")

unique(Plants_SpeciesBothSeasons$Season)
Plants_SpeciesBothSeasons$`D34SVCDT(permill)`<-as.numeric(Plants_SpeciesBothSeasons$`D34SVCDT(permill)`)

Plants_SpeciesBothSeasons$`D15NAir(permill)`<-as.numeric(Plants_SpeciesBothSeasons$`D15NAir(permill)`)

Plants_SpeciesBothSeasons$`D13CVPDB(permill)`<-as.numeric(Plants_SpeciesBothSeasons$`D13CVPDB(permill)`)

str(Plants_SpeciesBothSeasons$`D13CVPDB(permill)`)

Plants_MeansSd_BothSeasons<-Plants_SpeciesBothSeasons%>% 
  group_by(Species, Site, Season) %>% 
  summarize(n=n(),
            alpha = 0.05,
            D13C_mean = sum(`D13CVPDB(permill)`/n, na.rm=TRUE), 
            D13C_SD = sqrt(sum((`D13CVPDB(permill)`- (D13C_mean))^2)/(n-1)),
            D13C_StdError= standard_error(`D13CVPDB(permill)`),
            D15N_mean = sum(`D15NAir(permill)`/n, na.rm=TRUE),
            D15N_SD = sqrt(sum((`D15NAir(permill)`- (D15N_mean))^2)/(n-1)),
            D15N_StdError= standard_error(`D15NAir(permill)`),
            D35S_mean = sum(`D34SVCDT(permill)`/n, na.rm=TRUE),
            D35S_SD = sqrt(sum((`D34SVCDT(permill)`- (D35S_mean))^2)/(n-1)),
            D35S_StdError= standard_error(`D34SVCDT(permill)`)
            )

Plants_MeansSd_BothSeasons$D13C_StdError[is.nan(Plants_MeansSd_BothSeasons$D13C_StdError)]<-0

Plants_MeansSd_BothSeasons$D13C_StdError[is.na(Plants_MeansSd_BothSeasons$D13C_StdError)]<-0

Plants_MeansSd_BothSeasons$D13C_SD[is.nan(Plants_MeansSd_BothSeasons$D13C_SD)]<-0

Plants_MeansSd_BothSeasons$D15N_StdError[is.na(Plants_MeansSd_BothSeasons$D15N_StdError)]<-0

Plants_MeansSd_BothSeasons$D15N_SD[is.nan(Plants_MeansSd_BothSeasons$D15N_SD)]<-0

Plants_MeansSd_BothSeasons$D35S_StdError[is.na(Plants_MeansSd_BothSeasons$D35S_StdError)]<-0

Plants_MeansSd_BothSeasons$D35S_SD[is.nan(Plants_MeansSd_BothSeasons$D35S_SD)]<-0
```

### Plot S vs C
```{r}
#Don't need to filter any species out. We caught all the species in summer and fall (though not for each slough)

PlantPlot<-Plants_MeansSd_BothSeasons %>% ggplot(aes(D13C_mean, D35S_mean, color= Site)) + 
  geom_point(aes(color = Site, shape=Species), size=5) + 
  scale_shape_manual(values=rep(0:15, 1))+
  labs(title = "Plant Means And Standard Error Both Seasons") +
  theme_bw()+ 
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) + 
  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
PlantPlot
```

## All together now...
###I have to make zoops match the rest of them...
```{r}
Zoops_BothSeasons_MeansSd<-Zoops_SpeciesBothSeasons%>% 
  group_by(ZoopSpecies, Site, Season) %>% 
  summarize(n=n(),
            alpha = 0.05,
            D13C_mean = sum(`D13CVPDB(permill)`/n, na.rm=TRUE), 
            D13C_SD = sqrt(sum((`D13CVPDB(permill)`- (D13C_mean))^2)/(n-1)),
            D13C_StdError= standard_error(`D13CVPDB(permill)`),
            D15N_mean = sum(`D15NAir(permill)`/n, na.rm=TRUE),
            D15N_SD = sqrt(sum((`D15NAir(permill)`- (D15N_mean))^2)/(n-1)),
            D15N_StdError= standard_error(`D15NAir(permill)`),
            D35S_mean = sum(`D34SVCDT(permill)`/n, na.rm=TRUE),
            D35S_SD = sqrt(sum((`D34SVCDT(permill)`- (D35S_mean))^2)/(n-1)),
            D35S_StdError= standard_error(`D34SVCDT(permill)`))

Zoops_BothSeasons_MeansSd$D13C_StdError[is.na(Zoops_BothSeasons_MeansSd$D13C_StdError)]<-0

Zoops_BothSeasons_MeansSd$D13C_SD[is.nan(Zoops_BothSeasons_MeansSd$D13C_SD)]<-0

Zoops_BothSeasons_MeansSd$D15N_StdError[is.na(Zoops_BothSeasons_MeansSd$D15N_StdError)]<-0

Zoops_BothSeasons_MeansSd$D15N_SD[is.nan(Zoops_BothSeasons_MeansSd$D15N_SD)]<-0

Zoops_BothSeasons_MeansSd$D35S_StdError[is.na(Zoops_BothSeasons_MeansSd$D35S_StdError)]<-0

Zoops_BothSeasons_MeansSd$D35S_SD[is.nan(Zoops_BothSeasons_MeansSd$D35S_SD)]<-0
```

###Make columns match
```{r}
#Make columns match
Zoops_BothSeasons_MeansSd<-Zoops_BothSeasons_MeansSd %>% 
  rename(Species = ZoopSpecies)
Zoops_BothSeasons_MeansSd<- Zoops_BothSeasons_MeansSd[,c("Species", "Site", "Season", "D13C_mean", "D13C_StdError", "D15N_mean", "D15N_StdError", "D35S_mean", "D35S_StdError")]

Plants_MeansSd_BothSeasons<- Plants_MeansSd_BothSeasons[,c("Species", "Site", "Season", "D13C_mean", "D13C_StdError", "D15N_mean", "D15N_StdError", "D35S_mean", "D35S_StdError")]

Inverts_MeansSd_BothSeasons<- Inverts_MeansSd_BothSeasons[,c("Species", "Site", "Season", "D13C_mean", "D13C_StdError", "D15N_mean", "D15N_StdError", "D35S_mean", "D35S_StdError")]

FishMuscleData_SpeciesBothSeasons<- FishMuscleData_SpeciesBothSeasons[,c("Species", "Site", "Season", "D13C_mean", "D13C_StdError", "D15N_mean", "D15N_StdError", "D35S_mean", "D35S_StdError")]

FishLiverData_SpeciesBothSeasons<- FishLiverData_SpeciesBothSeasons[,c("Species", "Site", "Season", "D13C_mean", "D13C_StdError", "D15N_mean", "D15N_StdError", "D35S_mean", "D35S_StdError")]
```

### Food web with Fish Livers (no muscle)
```{r}
AvgData_BothSeasons_Livers<-rbind(Zoops_BothSeasons_MeansSd, Plants_MeansSd_BothSeasons, Inverts_MeansSd_BothSeasons, FishLiverData_SpeciesBothSeasons)

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("SAGO", "Myriophyllum spicatum", "Filamentous algae")]<- "SAV"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("Phragmites australis", "Typha angustifolia", "Schoenoplectus acutusa", "Schoenoplectus americanus")]<- "EV"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("Sarcocornia/Salicornia pacifica", "Calystegia sepium")]<- "Terrestrial"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Det"]<- "Det"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("SCP", "SG", "YFG", "SKG")]<- "Sculpin/Goby"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "ST"]<- "ST"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "TP"]<- "TP"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "SB"]<- "SB"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "BC"]<- "BC"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("Red swamp crayfish")]<- "Red swamp crayfish"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Harris mud crab"]<- "HMC"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Maeotias"]<- "Maeotias"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Exopalaemon"]<- "EXO"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Corbicula"]<- "Corbicula"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Crab Zoea"]<- "Crab Zoea"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% "Det"]<- "Det"

AvgData_BothSeasons_Livers$Class[AvgData_BothSeasons_Livers$Species %in% c("P. forbesi", "A. sinensis", "200-500 um", "100 um" ,">500 um")]<- "Zoop"

unique(AvgData_BothSeasons_Livers$Class)

AvgData_BothSeasons_Livers$Class<- factor(AvgData_BothSeasons_Livers$Class, levels = c("SB", "BC", "ST", "TP", "Sculpin/Goby", "Red swamp crayfish", "HMC", "Maeotias", "EXO", "Corbicula",  "Crab Zoea", "Zoop", "Terrestrial", "EV", "SAV", "Det")) #Changing level order 

Avg_BothSeasons_Livers<- AvgData_BothSeasons_Livers  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Season)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Season, shape = Class), size=5) +
 # scale_color_viridis_d()+
  labs(title = "All from Both Seasons - Fish livers") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean-D15N_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) #+facet_wrap(~factor(Season, levels=c("Summer", "Fall"))) #+ 
 # facet_wrap(~factor(Site))  theme(legend.position="none") + scale_color_viridis_d() +

Avg_BothSeasons_Livers

#Gotta split the seasons up. Too much data!
AvgData_Summer_Livers<-AvgData_BothSeasons_Livers %>% filter(Season %in% "Summer")
unique(AvgData_Summer_Livers$Species)
#filter(!(Species %in% c("Crab Zoea", "Gnorimosphaeroma insulare"))) + scale_color_brewer(palette = "Paired")

Avg_Summer_Livers<- AvgData_Summer_Livers  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Class)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Class, shape = Class), size=5) +
  scale_color_viridis_d()+
  labs(title = "All from Summer - Fish livers") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) #+facet_wrap(~Site) #+ 
 # facet_wrap(~factor(Site))  theme(legend.position="none") + scale_color_viridis_d() +

Avg_Summer_Livers

AvgData_Fall_Livers<-AvgData_BothSeasons_Livers %>% filter(Season %in% "Fall")

Avg_Fall_Livers.ShapesAndColors<- AvgData_Fall_Livers  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Class)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Class, shape = Class)) +
  scale_color_viridis_d()+
  labs(title = "All from Fall - Fish livers") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) #+ facet_wrap(~Site)
Avg_Fall_Livers.ShapesAndColors

Avg_Fall_Livers.Colors<- AvgData_Fall_Livers %>% ggplot(aes(D13C_mean, D35S_mean, color= Class)) + 
  geom_point(aes(color = Class), size=3) +
  labs(title = "All from Fall - Fish livers") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) #+ 
  #facet_wrap(~factor(Site))
Avg_Fall_Livers.Colors

AllData.Livers_Seasons<- AvgData_BothSeasons_Livers %>% ggplot(aes(D13C_mean, D35S_mean, color= Class)) + 
  geom_point(aes(color = Class, shape=Class), size=5) + 
  scale_shape_manual(values=rep(0:6, 7))+
  labs(title = "Food web with fish livers: Means And Standard Error from Summer and Fall") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) +  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
AllData.Livers_Seasons
```

### Striper plot
```{r}
AvgData_BothSeasons_Livers<-rbind(Zoops_BothSeasons_MeansSd, Plants_MeansSd_BothSeasons, Inverts_MeansSd, FishLiverData_SpeciesBothSeasons)

SB.Plot<- AvgData_BothSeasons_Livers %>% filter(Species %in% c("SB", ">500 um", "200-500 um", "A. sinensis", "P. forbesi", "100-500 um", "Mysid")) %>% ggplot(aes(D13C_mean, D35S_mean, color= Site)) + 
  geom_point(aes(color = Site, shape=Species), size=3) + 
  labs(title = "Striped Bass Livers and Zooplankton: Carbon, Sulfur Means And Standard Error from Summer and Fall") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean-D35S_StdError, ymax = D35S_mean+D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean-D13C_StdError, xmax = D13C_mean+D13C_StdError)) +  facet_wrap(~factor(Season, levels=c("Summer", "Fall")))
SB.Plot
```

## Food web with fish muscles (no livers)
```{r}
AvgData_BothSeasons_Muscles<-rbind(Zoops_BothSeasons_MeansSd, Plants_MeansSd_BothSeasons, Inverts_MeansSd_BothSeasons, FishMuscleData_SpeciesBothSeasons)

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("SAGO", "Myriophyllum spicatum", "Filamentous algae")]<- "SAV"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("Phragmites australis", "Typha angustifolia", "Schoenoplectus acutusa", "Schoenoplectus americanus")]<- "EV"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("Sarcocornia/Salicornia pacifica", "Calystegia sepium")]<- "Terrestrial"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Det"]<- "Det"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("SCP", "SG", "YFG", "SKG")]<- "Sculpin/Goby"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "ST"]<- "ST"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "TP"]<- "TP"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "SB"]<- "SB"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "BC"]<- "BC"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("Red swamp crayfish")]<- "Red swamp crayfish"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Harris mud crab"]<- "HMC"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Maeotias"]<- "Maeotias"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Exopalaemon"]<- "EXO"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Corbicula"]<- "Corbicula"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Crab Zoea"]<- "Crab Zoea"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% "Det"]<- "Det"

AvgData_BothSeasons_Muscles$Class[AvgData_BothSeasons_Muscles$Species %in% c("P. forbesi", "A. sinensis", "200-500 um", "100 um" ,">500 um")]<- "Zoop"

unique(AvgData_BothSeasons_Muscles$Class)

AvgData_BothSeasons_Muscles$Class<- factor(AvgData_BothSeasons_Muscles$Class, levels = c("SB", "BC", "ST", "TP", "Sculpin/Goby", "Red swamp crayfish", "HMC", "Maeotias", "EXO", "Corbicula",  "Crab Zoea", "Zoop", "Terrestrial", "EV", "SAV", "Det")) #Changing level order 

AvgData_Summer_Muscles<- AvgData_BothSeasons_Muscles %>% filter(Season %in% "Summer")

Avg_Summer_Muscles<- AvgData_Summer_Muscles  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Class)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Class, shape = Class), size=5) +
  scale_color_viridis_d()+
  labs(title = "All from Summer - Fish muscles") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) +facet_wrap(~Site) 
Avg_Summer_Muscles

AvgData_Fall_Muscles<- AvgData_BothSeasons_Muscles %>% filter(Season %in% "Fall")

Avg_Fall_Muscles<- AvgData_Fall_Muscles  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Class)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Class, shape = Class), size=5) +
  scale_color_viridis_d()+
  labs(title = "All from Fall - Fish muscles") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) +facet_wrap(~Site) 
Avg_Fall_Muscles

Avg_Muscles<- AvgData_BothSeasons_Muscles  %>%  ggplot(aes(D13C_mean, D35S_mean, color= Class)) + scale_shape_manual(values=rep(0:6, 7))+
  geom_point(aes(color = Class, shape = Class), size=5) +
  scale_color_viridis_d()+
  labs(title = "All from both seasons - Fish muscles") +
  theme_bw()+
  geom_errorbar(aes(ymin = D35S_mean - D35S_StdError, ymax = D35S_mean+ D35S_StdError))+
  geom_errorbarh(aes(xmin = D13C_mean - D13C_StdError, xmax = D13C_mean + D13C_StdError)) +facet_wrap(~factor(Season, levels=c("Summer", "Fall")) )
Avg_Muscles
```